Deployable Probabilistic Programming

### 2019-04-17 paper/paper.tex
small edits, more references

Models are of course not restricted to linear code, and may
comprise multiple methods, contain loops, conditional
statements, function and method calls, and recursion. Case
studies~(Section~\ref{sec:case-studies}) provide elaborated
model examples.

@@

In infergo, the inference is performed on a model. An Infergo
model is a data type and methods defined on the data type.
Inference algorithms accept a model object as an argument.
A model object usually encapsulates observations --- the data 
to which the parameter values are adapted.

@@

Building a production software system which employs
probabilistic inference as an integral part of prediction and
decision making algorithms is challenging. To address the
challenges, we proposed guidelines for implementation of a
deployable probabilistic programming facility. Further on, we
introduced Infergo, a probabilistic programming facility in Go,
as a reference implementation following the guidelines. Infergo
allows to program inference models in virtually unrestricted Go,
and to perform inference on the model using either supplied or
third-party algorithms. We demonstrated on case studies how
Infergo overcomes the challenges by following the guidelines.

A probabilistic programming facility similar to Infergo can be
added to most modern general programming languages, in
particular, those used in implementing large-scale software
systems, making probabilistic programming inference more
accessible in server-side applications. We described Infergo
design choices and implementation techniques in intent to
encourage broader adoption of probabilistic programming in
production software systems and ease implementation of similar
facilities in other languages and software environments.

>>>>

Models are of course not restricted to linear code, and may
comprise multiple methods containing loops, conditional
statements, function and method calls, and recursion. Case
studies~(Section~\ref{sec:case-studies}) provide elaborated
model examples.

@@

In Infergo, the inference is performed on a model. An Infergo
model is a data type and methods defined on the data type.
Inference algorithms accept a model object as an argument.
A model object usually encapsulates observations --- the data 
to which the parameter values are adapted.

@@

Building a production software system which employs
probabilistic inference as an integral part of prediction and
decision making algorithms is challenging. To address the
challenges, we proposed guidelines for implementation of a
deployable probabilistic programming facility. Further on, we
introduced Infergo, a probabilistic programming facility in Go,
as a reference implementation in accordance with the guidelines.
Infergo allows to program inference models in virtually
unrestricted Go, and to perform inference on the model using
either supplied or third-party algorithms. We demonstrated on
case studies how Infergo overcomes the challenges by following
the guidelines.

A probabilistic programming facility similar to Infergo can be
added to most modern general programming languages, in
particular, those used for implementation of large-scale software
systems, making probabilistic programming inference more
accessible in server-side applications. We described Infergo
design choices and implementation techniques in intent to
encourage broader adoption of probabilistic programming in
production software systems and ease implementation of similar
facilities in other languages and software environments.
